---
title: "OCTO-Twin review"
output:
  html_document:
    css: ~/GitHub/terminal-decline/libs/css/sidebar-simple-wide.css
    highlight: kate
    keep_md: yes
    theme: flatly
    toc: yes
---


<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 7, 
  fig.width = 11, 
  out.width = "1200px",
  fig.path = 'figure_rmd_octo/',     
  dev = "png",
  dpi = 300
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./reports/basic-review/review-octo.R") 
```

This reports reivews the basic information about the fitted model from _OCTO-Twin_ study.

<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echoChunks, message=FALSE}
```


<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks, message=FALSE}
```


<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put code in here.  It doesn't call a chunk in the codebehind file.
```

This reports interacts with the _data transfer object_ created by the `./manipulation/0-ellis-island.R` script. 
<!-- Load the datasets.   -->
```{r load-data, echo=echoChunks, results='hide', message=FALSE}
```

<!-- Inspect the datasets.   -->
```{r inspect-data, echo=echoChunks, results='hide', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echoChunks, results='show', message=FALSE}
```

# Descriptives

This section shows descriptive graphs of the variables that were used in computation of model solution. The displayed data came from the `SAVEDATA` command.
```{r descriptives, echo=echoChunks, results='asis', message=FALSE, warning=F,out.width="800px"}
```

# Solution

This section contains tabulated output from the `.out` file, generated by _Mplus_ during estimation.
```{r solution-table, echo=echoChunks, results='asis', message=FALSE, warning=F}
```

# Classes

This section contains information about latent classes and the properties of their separation.

## Membership
```{r class-separation-info, echo=echoChunks, results='show', message=FALSE, warning=F,out.width="800px"}
```

## Graph legend

The graphs in the remainder of this section display class separation and explore its relationship with the predictors. 
```{r class-separation-graphs, echo=echoChunks, results='asis', message=FALSE, warning=F}
```

# Observed

This sections contain observed trajectories of the main criterion (`MMSE`)
```{r observed-trajectories, echo=echoChunks, results='asis', message=FALSE, warning=F}
```

# Modeled
This section contains trajectories of the criterion **RECONSTRUCTED** from the factor scores. The formula that was used to arrive at the predicted values is:
```
modeled_value = level + slope*time + quadratic*time
```
where `level`,`slope`,and `quadratic` are individual facto scores estimated by the model, and `time` is time in study.
```{r modeled-trajectories, echo=echoChunks, results='asis', message=FALSE, warning=F}
```

```{r session-info, echo=FALSE}
cat("Report rendered by", Sys.info()["user"], "at", strftime(Sys.time(), "%Y-%m-%d, %H:%M %z"))
sessionInfo()
```